---
title: "matchGADM usage"
author: "Katy Gaythorpe and Arran Hamlet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

`matchGADM` is a package for converting between shapefiles whether they be from gadm or otherwise.
The result is a data frame of proportions from old to new in order to ease moving data such as population sizes between old and new shapefiles.

# Example usage

We load some example data to show potential usage for the main functions, `area_match` and `area_match_multi`.

```{r , eval=FALSE}

library(maptools)
library(matchGADM)
library(rgdal)
library(rgeos)

### VERSIONS ### --------------------------------------------------------------------------------------------
old_version = "2"
new_version = "36"

### IMPORT ###  ---------------------------------------------------------------------------------------------
shp1_old = readShapePoly(paste0("data/gadm", old_version, "/Africa_adm1.shp"))
shp1_new = readOGR(paste0("data/gadm", new_version, "/Africa_adm1.shp"),
                   use_iconv = TRUE, encoding = "UTF-8")

names(shp1_new)[1] = "ISO"
names(shp1_new)[3] = "ID_1"

ptm <- proc.time()
comb_df = area_match_multi(shp1_old, shp1_new)
proc.time() - ptm

```

One could also use `area_match` in the same way if the boundaries of countries are known to have changed; however, this will be slower to implement.

